A Lightweight AI-based Approach For Drone Jamming Detection

### 2024-11-23 article.tex
Edited related works sections and added comparison table

@@

@@

>>>>

The authors of \cite{JammingDetectionDrones-Greco} compare the use of Multi-Layer Perceptrons (MLPs) and Decision Trees for the detection of jamming attacks in drone networks, showing that both methods are able to achieve good detection performance.

@@

Table \ref{tab:method_comparison} shows a summary of the detailed approaches for jamming detection in scientific literature.

\begin{table}[H]
    \caption{Existing approaches for jamming detection in scientific literature\label{tab:method_comparison}}
    \newcolumntype{C}{>{\centering\arraybackslash}X}
    \begin{tabularx}{\textwidth}{CCCC}
    \toprule
    \textbf{Reference} & \textbf{Data Source} & \textbf{Method} & \textbf{Metrics} \\
    \midrule
    \cite{JammingDetectionML-Arjoune} & Simulation & Random Forest & BPR, PDR, RSS, CCA \\
    \cite{JammingDetectionIoT-Hussain} & Real data & CNN & RSS \\
    \cite{JammingDetectionML-Arjoune} & Simulation & Linear SVM & BPR, PDR, RSS, CCA \\
    \cite{HybridJammingDetection-Hong} & Real data & DT + IF & PDR, BPR, SNR, RSSI \\
    \cite{JammingDetectionDrones-Greco} & Real + Simulated data & DT + MLP & Throughput, PDR, RSSI \\
    Our solution & Real data & IF & RSS \\
    \bottomrule
    \end{tabularx}
\end{table}

@@

\bibitem[Greco et al.(2021)]{JammingDetectionDrones-Greco}
Greco, C.; Pace, P.; Basagni, S.; Fortino, G. Jamming detection at the edge of drone networks using Multi-layer Perceptrons and Decision Trees. {\em Applied Soft Computing} {\bf 2021}, {\em 111}, 107806. https://doi.org/10.1016/j.asoc.2021.107806. Available online: \url{https://www.sciencedirect.com/science/article/pii/S1568494621007274}.
